PM Mungbean meta-analysis

### 2020-07-21 02_Preliminary_analysis.Rmd
Add missing pipe

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested")%>%
   select(Year,Value)
   ggplot(aes(y = Value, x = Year))+
   geom_point()+
   geom_smooth()

>>>>

beans %>%
   filter(Item == "Beans, dry",
          Element == "Area harvested")%>%
   select(Year,Value)%>%
   ggplot(aes(y = Value, x = Year))+
   geom_point()+
   geom_smooth()
